Notes
=====

Just a place to put some notes and thoughts and test out some code.

We are picturing a pdf with the orange IMAGINE light bulb logo at low saturation
as the page background and the IMAGINE word logo up top. 

Intro: What is the microbiome? What is the study?

Fig 1: A: a ggplot word cloud of genera coloured by family with a low-saturation 
colon diagram in the background. B: a taxa bar chart at the genus level, but 
ordered and coloured within family. Consider giving mean and individual. If mean,
surround with at least four diverse samples to show the range

Fig 2: "You are here" PCoA plot with ~1000 individuals in the background and the
participant's sample coloured and foregrounded. Maybe with a taxa pie chart
instead of a dot? But probably not

Descriptions: The top 3 families in each sample get their descriptions placed at
the bottom of the page. Provide a link to a website that has descriptions of all
families present in the top 10 of everyone.

Setup
-----

Inset Plots
-----------

I found a [stack overflow question about this](https://stackoverflow.com/questions/5219671/it-is-possible-to-create-inset-graphs).

To do inset graphs (e.g. superimpose the bar graph over the 
scatterplot), we use `grid::viewport()`` apparently. Link 
[here](https://groups.google.com/g/ggplot2/c/XIkND56UUWY).

Another (better?) option is to use the `egg` library: 

### Inset the bar plot

```{r}
library(egg)

ord_df = plot_ordination(ps_rel_filt, bray_ord_ps, justDF = TRUE)
barplt2 = plot_tax_bar(ps_gen_df, rank = 'Family', sample = 'Study_ID',
                       legloc = 'none') +
    theme(axis.title = element_blank(),
          axis.ticks = element_blank(),
          axis.text = element_blank(),
          line = element_blank(),
          rect = element_blank())
barplt2
xpos = ord_df['IMG106', 'Axis.1']
ypos = ord_df['IMG106', 'Axis.2']
head(ord_df)
ord_plt + annotation_custom(ggplotGrob(barplt2),
                            xmin = xpos+0.0001,
                            ymin = ypos+0.0001,
                            xmax = xpos+0.07,
                            ymax = ypos+0.1)
```

```{r}
library(ggwordcloud)
head(ps_gen_df)

ps_wc = (ps_gen_df
         %>% group_by(Genus)
         %>% summarize(Abundance = sum(Abundance))
         %>% filter(Genus != 'Other'))

wcplt = ggplot(ps_wc, aes(label = Genus, size = Abundance)) +
    geom_text_wordcloud() +
    theme_minimal()
wcplt

set.seed(1)
ggwordcloud(words = ps_wc$Genus, freq = ps_wc$Abundance*10000, min.freq = 0,
            ordered.colors = TRUE) +
    scale_colour_manual(values = tax_colours)
```

