---
output: 
    pdf_document:
        includes:
            in_header: header.tex
            before_body: body.tex
        keep_tex: true
colorlinks: true
date: "2023-05-26"
---

```{r Setup, include=FALSE, message=FALSE, warning=FALSE}
knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE)
library(tidyverse)
library(phyloseq)
library(AfterSl1p)
library(ggwordcloud)
library(cowplot)
library(ggpubr)
load('data/all_processed.RData')

# set the sample
samp = 'REPLACEME'
my_df = filter(ps_df, Study_ID == samp)
gut_img_sml = png::readPNG('img/gut_for_word_cloud.png')
gut_img_lrg = png::readPNG('img/gut_for_word_cloud_cover.png')
```

```{r, child = 'ChildDocs/WordCloudPlt.Rmd'}
```

```{r, child = 'ChildDocs/BrayPlt.Rmd'}
```

```{r, child = 'ChildDocs/Title.Rmd'}
```


\pagenumbering{arabic}

```{r, child = 'ChildDocs/Introduction.Rmd'}
```

\newpage

\vspace*{\fill}

```{=latex}
\begin{multicols}{2}
```

\section{Your Sample}
\begin{small}
This \textbf{taxonomic bar chart} shows your personal fecal bacterial community. 
Bacteria are grouped into \textbf{families} based on how closely related
they are.

The bar chart is stacked from most abundant bacterial family on the 
bottom, to least abundant on the top, with very low-abundance 
bacteria grouped together as "Other". Next to it is a chart showing
the average community of all the people who participated in the study,
and across the bottom are four anonymous individuals chosen to show
the range of variation in this study. As you can see, it's quite wide!

Below are the names of the most common bacterial families found in this study.
\end{small}
\columnbreak


```{r BarPlotDisplay, fig.width=5, fig.height=5}
c1
```

```{=latex}
\end{multicols}
```
```{r, fig.height=2, fig.width=6, fig.align='center'}
plot_grid(legnd)
```
\vspace*{\fill}
\newpage

```{=latex}
\begin{multicols}{2}
\raggedcolumns
```

```{r WdCldSmlDisplay, fig.width=4, fig.height=5, fig.align='center'}
wcplt
```

\columnbreak

\vspace*{1cm}
\section{$\boldsymbol{\leftarrow}$ More Detail}
\begin{small}
This word cloud shows your personal bacterial community at a finer 
level of detail. Within each family, bacteria can be subdivided into 
several \textbf{genera} (singular, \textbf{genus}). The size of each word
represents the relative abundance of that genus, and the colour shows
which family that genus comes from.
\end{small}
\vspace*{\fill}


```{=latex}
\end{multicols}
```

```{=latex}
\begin{multicols}{2}
\raggedcolumns
```

\vspace*{\fill}
\section{You Are Here $\boldsymbol{\rightarrow}$}
\begin{small}
There are nearly 4,000 people participating in this study so far! We have 
graphed everyone together based on how similar or different their gut
microbiomes were. In the next graph, points that are closer together
are more similar to each other, and points that are farther apart are
more different. Your sample is shown in green. Remember that your 
position in this graph doesn't say anything about how healthy your
gut microbiome is. As we've seen above, there is a wide range of 
normal variation in the human gut.
\end{small}

\vspace*{\fill}
\columnbreak


\vspace*{1cm}
```{r BrayPlotDisplay, fig.wdith=3, fig.height=6, fig.align='center'}
my_bray_plt
```

\vspace*{\fill}
```{=latex}
\end{multicols}
```

\newpage

\section{Your Bacterial Families}

Everyone's microbiome is different. In your microbiome, the four most
abundant bacterial families were \textit{Lachnospiraceae}, 
\textit{Ruminococcaceae}, \textit{Bacteroidaceae}, and 
\textit{Oscillospiraceae}. Here is a little bit of information
about what functions these four familes perform in the gut.


```{r, child = 'FAM1'}
```

```{r, child = 'FAM2'}
```

```{r, child = 'FAM3'}
```

```{r, child = 'FAM4'}
```

